Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-09-27 paper/paper.Rmd
rephrased statement on user-contributed methods

Contributions of new or missing spatiotemporal resampling methods is encouraged and can be done directly in \pkg{mlr3spatiotempcv}.
Contributors can orient themselves by looking at the already implemented methods with respect to class structure, active bindings and methods.

>>>>

Users are encouraged to contribute new or missing spatiotemporal resampling methods directly to \pkg{mlr3spatiotempcv}.
The already implemented methods can be inspected to get to know the class structure, active bindings and methods.
